Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-03-13 Scripts/Initial_Analysis.Rmd
control panel updates

```{r EstPropChange}

@@

```{r funEstTransIndex, eval= T ,echo = T,warning = F,message = F}

@@

```{r load_data_per_ensamble, eval = T, echo = T}

@@

Spp_list <- c(600004,600005)
iyr <- 1951
fyr <- 2099
data_type <- "Catch"
ensamble_list = c(102,103)
Path <- paste(data_path,"DBEM/",sep="")
world_grid <- tibble(index = seq(1,259200,1))
Neighbours <- read_excel("Temporal_Data/Spatial/EEZ_Neighbour_List.xlsx") %>% 
  clean_names()
Transboundary_spp <- read.csv("~/GitHub/TransEmergence/Temporal_Data/Species/Transboundary_spp.csv") %>% clean_names()

>>>>

```{r EstPropChange, eval = T, echo = F}

@@

```{r funEstTransIndex, eval= F ,echo = T,warning = F,message = F}

@@

```{r load_data_per_ensamble, eval = F, echo = T}

@@

Spp_list <- read.csv(paste(data_path,"Species/Species_list.csv",sep="")) %>% clean_names()
iyr <- 1951
fyr <- 2099
data_type <- "Catch"
ensamble_list = seq(102,111,1)
Path <- paste(data_path,"DBEM/",sep="")
world_grid <- tibble(index = seq(1,259200,1))
Neighbours <- read_excel(paste(data_path,"Spatial/EEZ_Neighbour_List.xlsx",sep="")) %>% 
  clean_names()

Transboundary_spp <- read.csv(paste(data_path,"Species/Transboundary_spp.csv",sep="")) %>% clean_names()
